Declarative Deployment Reconfiguration of Pulverised Collective Adaptive Systems at Runtime \thanks{ This work has been supported by the Italian PRIN Project COMMON-WEARS (2020HCWWLP) and the EU/MUR FSE REACT-EU PON R\&I 2014-2020. }

### 2023-05-21 paper-2023-acsos-pulverization.tex
promote @nicolasfara's meta, tag @metaphori for reference and double check

To show the potential benefit of automatic reconfiguration in \acp{cas},
we consider a large-scale scenario where a crowd of people is attending an event in a city
to participate in a collective activity whose computational weight is relevant,
for instance,
a tournament of a geo-located game similar to Ingress\footnote{\url{https://www.ingress.com/}}
or Pokémon Go\footnote{\url{https://pokemongolive.com/}}).
%
We suppose the application to be pulverised
and its behaviour to be able to run either on smartphones or in the cloud.
%
We assume the event starts with users in random positions in the city,
where their respective recharging station is located.
%
The game requires physically moving into the city,
reaching a \ac{poi} and performing some operations there.
%
We assume users with low battery to turn off the application and move to their start station to recharge the device
before rejoining the game.
%
The application is pulverised,
and its behaviour can execute either on the device or in the cloud.
%
We configure the framework to move the behaviour to the cloud when the battery level
(measured as a percentage of the maximum charge)
is below a threshold $\lambda$,
and to move it back to the device when the battery is charged enough to cross a threshold $\upsilon$
(stable configuration have $\upsilon{}>\lambda$,
otherwise the system continuously moves the behaviour between cloud and devices).
%
We thus indicate any configuration with $\Updownarrow^{\upsilon}_{\lambda}$,
with the exception of two cases:
$\upsilon, \lambda > 100$, forcing the behaviour to be always in the cloud, that we indicate with $\Uparrow$;
and $\upsilon, \lambda < 0$, forcing the behaviour to be always on the device, that we indicate with $\Downarrow$.
%
We are interested in the following metrics:
%
\begin{itemize}
    \item $P_{devices}$ ($kW$), the average device power consumption, a proxy for the battery life;
    \item $P_{cloud}$ ($kW$), the average power consumption of the cloud, if added to $P_{devices}$
    provides the total power consumption
    (hence, assuming a non-carbon-neutral energy mix, it is also a proxy for the carbon footprint);
    \item Distance ($km$), the total distance walked by the participants, a proxy for the \ac{qos},
    as users that need to stop and recharge stop walking;
    \item $\$_{cloud}$ (\$), the price paid to keep the required cloud instances up and running.
\end{itemize}

>>>>

To show the potential benefit of automatic reconfiguration in \acp{cas},
we consider a large-scale scenario where a crowd of people is attending an event in a city
to participate in a collective activity whose computational weight is relevant,
for instance,
a tournament of a geo-located game similar to Ingress\footnote{\url{https://www.ingress.com/}}
or Pokémon Go\footnote{\url{https://pokemongolive.com/}}).
%
We suppose the application to be pulverised
and its behaviour to be able to run either on smartphones or in the cloud.
%
We assume the event starts with users in random positions in the city,
where their respective recharging station is located.
%
The game requires physically moving into the city,
reaching a \ac{poi} and performing some operations there.
%
We assume users with low battery to turn off the application and move to their start station to recharge the device
before rejoining the game.
%
The application is pulverised,
and its behaviour can execute either on the device or in the cloud.
%
We configure the framework to move the behaviour to the cloud when the battery level
(measured as a percentage of the maximum charge)
is below a threshold $\lambda$,
and to move it back to the device when the battery is charged enough to cross a threshold $\upsilon$
(stable configuration have $\upsilon{}>\lambda$,
otherwise the system continuously moves the behaviour between cloud and devices).
%
We thus indicate any configuration with $\Updownarrow^{\upsilon}_{\lambda}$,
except for two cases:
$\upsilon, \lambda > 100$, forcing the behaviour to be always in the cloud, that we indicate with $\Uparrow$;
and $\upsilon, \lambda < 0$, forcing the behaviour to be always on the device, that we indicate with $\Downarrow$.
%
We are interested in the following metrics:
%
\begin{itemize}
    \item $P_{devices}$ ($kW$), the average device power consumption, a proxy for the battery life;
    \item $P_{cloud}$ ($kW$), the average power consumption of the cloud, if added to $P_{devices}$
    provides the total power consumption
    (hence, assuming a non-carbon-neutral energy mix, it is also a proxy for the carbon footprint);
    \item Distance ($km$), the total distance walked by the participants, a proxy for the \ac{qos},
    as users that need to stop and recharge stop walking;
    \item $\$_{cloud}$ (\$), the price paid to keep the required cloud instances up and running.
\end{itemize}
